### 2016-09-22 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to gas burner report made during full read through

% \cleardoublepage
% \phantomsection
% \addcontentsline{toc}{chapter}{List of Tables}
% \listoftables

@@

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
% [Brief Introduction of FRD at NIST, ventilation, etc.]
The Fire Fighting Technology Group of the Fire Research Division at the National Institute of Standards and Technology (NIST) develops and applies technology, measurements, and standards to improve the understanding of fire behavior, prevention and suppression, which ultimately enables advances in fire fighting operations, firefighter equipment, fire suppression, fire investigations, and disaster response. One function of the group is to conduct research to enhance the understanding of fire fighting tactics and how they affect the fire environment.

@@

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics presented in the follow sections.

@@

Three propane burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment. Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure. Propane was supplied to the burners during all experiments. The flow of propane to each burner was controlled by a high-precision turn valve, and the total displaced gas volume was measured using a rotary gas meter.

\begin{figure}[!ht]
	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
	\caption[Three propane burners used as fire source.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls on the first floor provided the fire source for the experiments.}
	\label{fig:burners}
\end{figure}

@@

Each bare-bead thermocouple array was composed of eight thermocouples. Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}. The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent, 320~mm (12.75~in) above the compartment ceiling. The array contained three probes centered between the east and west sides of the vent. The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}. The total heat flux gauge/radiometer pairs were aimed to view the ceiling. Gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.

@@

 & HF\_2\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\

@@

\subsubsection{Compartment Dimensions}
Each length measurement was taken carefully. Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}. However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range. Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}. Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\%.

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty. Maximum percent error has been reported to be as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.

@@

\subsubsection{Gas Sampling}
The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}. Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with gas concentration measurements~\cite{Lock:1}.

\subsubsection{Pressure Transducers}
Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers. The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}. The total expanded uncertainty was estimated at 10~\%.

\subsubsection{Bi-Directional Probes}
Bi-directional probes and single thermocouples were used to measure the velocity. The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above. A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe. The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath. A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}. The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18~\%.

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}. A volumetric flow rate was calculated from the gas meter measurements and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm12$~\%.

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests 2--6, were conducted in the East Structure. Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for each experiment. The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

\subsection{Tests 2--4}
Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 61~cm (24~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.

\begin{table}[!ht]
\caption{Heat Release Rates for Tests~2--4}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 560 & 1080 & 1470 & 1070 & 550 \\
Test 3 				& 530 & 1040 & 1470 & 1050 & 520 \\
Test 4				& 580 & 1140 & 1580 & 1130 & 580 \\
\bottomrule
\end{tabular}
\label{table:HRR_Tests_2-4}
\end{table}

@@

\subsection{Tests 5 \& 6}
The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved repeating a specific set of events three times in a row. To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.

@@

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
Test 22				&     	1240 	  \\
Test 23				&     	1290 	  \\
Test 24				& 	    1270 	  \\
Test 25				&     	1270 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed a nearly identical procedure to change the ventilation. The starting configuration for Test~22 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~23 had the same door in the closed position. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.95\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\subsection{Tests~24 \& 25}
Similar to Tests~22 and 23, Tests~24 and 25 followed a nearly identical test procedure. The starting configuration for Test~24 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~25 had the same door in the closed position. Also, the stairwell door was unable to completely close. When it was in the ``closed'' position at the beginning of each test, there was a 152~mm (6~in) gap between the door and its frame. Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.

@@

\chapter{Summary}
\label{chap:Summary}
Nine full-scale fire tests were conducted in two residential-sized structures to examine how changing ventilation patterns within a structure affects the fire environment. The fire source for each experiment was provided by a set of three diffusion flame burners with propane as the fuel. Various doors and vents were opened and closed during each test to affect the ventilation within the structure. A PPV fan was also used during some of the experiments to change the ventilation patterns. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during each experiment. The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire for each test.

>>>>

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

@@

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
The Fire Fighting Technology Group of the Fire Research Division at the National Institute of Standards and Technology (NIST) develops and applies technology, measurements, and standards to improve the understanding of fire behavior, prevention and suppression, which ultimately enables advances in fire fighting operations, firefighter equipment, fire suppression, fire investigations, and disaster response. One function of the group is to conduct research to enhance the understanding of fire fighting tactics and how they affect the fire environment.

@@

\section{Instrumentation}
\label{sec:Instrumentation}
The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample. Then, the dry gas samples were piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured. A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics presented in the follow sections.

@@

Three diffusion flame burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment. Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure. Propane was supplied to the burners during all experiments. The flow of propane to each burner was controlled by a high-precision turn valve, and the total displaced gas volume was measured using a rotary gas meter.

\begin{figure}[!ht]
	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
	\caption[Three propane burners used as the fuel source.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls on the first floor that provided the fire source for the experiments.}
	\label{fig:burners}
\end{figure}

@@

Each bare-bead thermocouple array was composed of eight thermocouples. Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in the exterior doorways of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}. The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent, 320~mm (12.75~in) above the compartment ceiling. The array contained three probes centered between the east and west sides of the vent. The position of each probe and thermocouple pair relative to the south wall of the vent is listed in the channel list presented in Table~\ref{table:east_channel_list}. The total heat flux gauge/radiometer pairs were aimed to view the ceiling. Gas samples were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing. The height of each individual sensor in the sensor arrays is listed in Table~\ref{table:east_channel_list}.

@@

The thermocouple arrays and the bi-directional probe plus solid thermocouple arrays contained eight sensors per array. Gas samples were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors was located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 contained one sensor facing the ceiling and another facing the stairway door. The height of each individual sensor in the sensor arrays is listed in the channel list found in Table~\ref{table:west_channel_list}.

@@

 & HF\_2\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing N wall (horizontal) \end{tabular} & Total heat flux \\

@@

\subsubsection{Compartment Dimensions}
Each length measurement was taken carefully. Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}. However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range. Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}. Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\% for length measurements.

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself as determined by the wire manufacturer is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty. Maximum percent error has been reported to be as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty associated with the temperature measurements is $\pm$15~\%.

@@

\subsubsection{Gas Sampling}
The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}. Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with the gas concentrations~\cite{Lock:1}.

\subsubsection{Pressure Transducers}
Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers. The transducers were factory calibrated, and the zero and span of each were checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}. The total expanded uncertainty is estimated at 10~\%.

\subsubsection{Bi-Directional Probes}
Bi-directional probe and single thermocouple pairs were used to measure gas velocity. The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above. A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe. The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath. A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}. The total expanded uncertainty for gas velocity measurements is estimated to be $\pm$18~\%.

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error of the meter as $\pm$2~\%~\cite{Romet:2014}. A volumetric flow rate was calculated from the gas meter volume readings and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm12$~\%.

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests~2--6, were conducted in the East Structure. Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for Tests~2--4 and Tests~5--6, respectively. The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for one, two, and three burners, and for Tests~5 and 6, a single heat release rate for three burners is reported.
% Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

\subsection{Tests 2--4}
Tests~2--4 followed a nearly identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 0.61~cm (2.0~ft) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport the propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed, and gypsum board was used to cover the doorway.

\begin{table}[!ht]
\caption{Heat Release Rates for Tests~2--4}
\begin{tabular}{lccc}
 \toprule
 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} \textbf{One} \\ \textbf{Burner On} \end{tabular} 
					&	\begin{tabular}{c} \textbf{Two} \\ \textbf{Burners On} \end{tabular}
					&	\begin{tabular}{c} \textbf{Three} \\ \textbf{Burners On} \end{tabular} \\
 \midrule
Test 2 				& 560 & 1080 & 1470 \\
Test 3 				& 530 & 1040 & 1470 \\
Test 4				& 580 & 1140 & 1580 \\
\bottomrule
\end{tabular}
\label{table:HRR_Tests_2-4}
\end{table}

% \begin{table}[!ht]
% \caption{Heat Release Rates for Tests~2--4}
% \begin{tabular}{lccccc}
%  \toprule
%  					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
% \textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
% 					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
% 					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
% 					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
% 					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
%  \midrule
% Test 2 				& 560 & 1080 & 1470 & 1070 & 550 \\
% Test 3 				& 530 & 1040 & 1470 & 1050 & 520 \\
% Test 4				& 580 & 1140 & 1580 & 1130 & 580 \\
% \bottomrule
% \end{tabular}
% \label{table:HRR_Tests_2-4}
% \end{table}

@@

\subsection{Tests 5 \& 6}
The procedures for Tests~5 and 6 are outlined in Figs.~\ref{fig:east_test_5} and \ref{fig:east_test_6}, respectively. Both tests involved repeating a specific set of events three times in a row. To avoid listing the identical actions three separate times in the ``event'' column of the tables, each repetition of events is denoted as a ``sequence'' (abbreviated as ``seq.''), and each table contains three columns of times---one for each sequence.

@@

\begin{table}[!ht]
\caption{Heat Release Rates for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& \textbf{All Burners On} \\
 \midrule
Test 22				&     	1240 	  \\
Test 23				&     	1290 	  \\
Test 24				& 	    1270 	  \\
Test 25				&     	1270 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed a nearly identical procedure. The starting configuration for Test~22 had the second story south exterior door in the opened position, while the starting configuration for Test~23 had the same door in the closed position. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 0.61~m (2.0~ft) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.95\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\subsection{Tests~24 \& 25}
Like Tests~22 and 23, Tests~24 and 25 followed a nearly identical procedure. The starting configuration for Test~24 had the south exterior door on the second level in the opened position, while the starting configuration for Test~25 had the same door in the closed position. During both tests, the stairwell door was unable to completely close. When it was in the ``closed'' position at the beginning of each test, there was a 152~mm (6.0~in) gap between the door and its frame. Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25. A 0.61~m (2.0~ft) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.

@@

\chapter{Summary}
\label{chap:Summary}
Nine full-scale fire tests were conducted in two residential-sized structures to examine how changing ventilation patterns within a structure affects the fire environment. The fire source for each experiment was provided by a set of three diffusion flame burners with propane as the fuel. Various doors and vents were opened and closed during each test to change ventilation within the structure. A PPV fan was also used during some of the experiments to change the ventilation patterns. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during the experiments. The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire during each test.
